Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-16 02_Paper/paper.tex
worked on section 2.2 and bib

>>>>

Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
This offers a wide range of applications. In the context of industrial or production enviroments, this includes for example 
predictive maintenance of machines, the increase of organization performance, production efficiency or improving product design %Quellen einfügen.
Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
etablished quality control methods, in terms of speed, accuracy and time delay.
%...
